I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-19 Reports/tech_report1.tex
update report

>>>>

The output binary file of layer 7 is \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_21_10_10_33.b|.

The output of binary file of layer 9 is: \verb*|Diamond_record_5_100_dictionary_with_end_layer9_2024_03_23_21_53_04.b|

The output of binary file of layer 11 is:

\verb*|Diamond_record_5_100_dictionary_with_end_layer11_2024_03_24_23_38_45.b|

### 2024-04-19 lipics-master/experiments.tex

We now turn to evaluating the choice of ReLU nodes in two layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define:
%\vspace{-0.2cm}
$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
%\vspace{-0.2cm}

and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$. We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.

>>>>

We now turn to evaluating the choice of ReLU nodes in two layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define:
%\vspace{-0.2cm}
$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ and the associated $comp(b)=\sum_{b' \in Z} comp(b,b') + comp(b',b)$. We then select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$. {\color{red} The intuition behind the formula is simple: $\val_{\vx}(a)weight(abcd)$ is the naive contribution from node $a$ to the target $d$. And the min of two paths is a natural number for the strength of compensating: if one of them is very small, the effect of compensating will also be very small.}

### 2024-04-19 lipics-master/proofs.tex
update contents
update

{\color{red}Notice that above definitions only involve weights, not bias. From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}

@@

@@

We now prove Theorem \ref{th2} under the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target). This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected.

>>>>

{\color{red}Notice that above definitions only involve weights, and do not use bias. From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}

@@

{\color{red} As we mentioned before, this proof does not have any requirements on the bias.}

@@

We now prove Theorem \ref{th2} under the fairly light {\em well-connected hypothesis} (H1) that the DNN is such that for every 2 (not necessarily disjoint) paths $\rho_1,\rho_2$ with non-zero weight with the same source $m$ and the same target $n$ at least 2 layers apart, there exists another path $\rho_3$ from $m$ to $n$ (with non zero-weight) totally disjoint from $\rho_1$ and $\rho_2$ (except at the source and target). This hypothesis is used to remove corner cases which will not happen in actual DNNs, which all are well-connected. {\color{red} Moreover, this hypothesis only matters in the theoretical proof. This is because in practice, paths with zero or very small weights will have very small effect on the output, and very small effect on the models, too.  Usually these paths will not be considered.}

### 2024-04-19 lipics-master/relatedwork.tex

When examining ERAN-Deeppoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate. This is a novel insight, to our knowledge. DeepPoly abstracts the weight of every node using two functions: an upper function and a lower function. While the upper function is fixed, the lower function offers two choices. In Proposition \ref{LP}, we demonstrate that the LP relaxation precisely matches the intersection of these two choices. Consequently, it is more accurate than DeepPoly but less efficient. \CMP is considerably more precise than DeepPoly (it refines LP), albeit less efficiently.

>>>>

When examining ERAN-DeepPoly \cite{deeppoly}, which efficiently computes bounds on values, we establish that LP encoding is unequivocally more accurate. This is a novel insight, to our knowledge. DeepPoly abstracts the weight of every node using two functions: an upper function and a lower function. While the upper function is fixed, the lower function offers two choices. In Proposition \ref{LP}, we demonstrate that the LP relaxation precisely matches the intersection of these two choices. Consequently, it is more accurate than DeepPoly but less efficient. \CMP is considerably more precise than DeepPoly (it refines LP), albeit less efficiently.
